CDSR Human Data/Modelling Paper

### 2013-09-12 code/scenarios/cdsr/trunk/papers/ACS2013/main.tex
jk revised section 3

Both of these research questions address the fundamental claim that CDSRs are contextually defined. Question 1 addresses this claim by examining variation in CDSR placement within different situations. In a context exhibiting clear contextual clues (e.g. determining a safe zone in a battle context where all information is known and battle formations are well-defined) one would expect high agreement in human identification of the CDSR. In a less well-defined context, one might expect little to no agreement between human communicators.  Research question 2 addresses the contextual nature of CDSRs in terms of whether or not the variation in the location and extent of a CDSR systematically follow the variations  in the given context.

@@

To examine these questions, we developed two experimental tasks:
\begin{itemize}
	\item{Task 1:} subjects were presented with a visual representation of a spatial scene plus a linguistic description containing a CDSR and were tasked with drawing a polygon on the visual stimuli such that it defined the extent of the CDSR in the scene (or stated there was no such region).
	\item{Task 2:} subjects were presented with a visual representation of a spatial scene with a marked location and an accompanying spatial description and were asked to rate how well it fit with their understanding of the CDSR on a five point likert scale.
\end{itemize}

@@

\subsection{Participants and Procedure}
Using these stimuli pairs, we developed an online experiment with two different types of trials to explore our initial questions. 43 undergraduate students from two different third level institutes took part in the study. To control for sequence effects the presentation order of the trials were randomised for each participant as was the order of the stimuli presented within each trial.

>>>>

Both of these research questions address the fundamental claim that CDSRs are contextually defined. Question 1 addresses this claim by examining: (a) whether or not a CDSR is always applicable in a given enviroment (more bluntly, does a classroom always have a front or is this dependent on the configuration of objects in the room), and (b) the variation in CDSR placement and size within different context. Research question 2 addresses the contextual nature of CDSRs in terms of whether or not the variation in the location and extent of a CDSR systematically follow the variations  in the given context.

%In a context exhibiting clear contextual clues (e.g. determining a safe zone in a battle context where all information is known and battle formations are well-defined) one would expect high agreement in human identification of the CDSR. However, in the same environment (classroom, geographic location) but with less well-defined context, one might expect little to no agreement between human communicators.

@@

To examine these questions, we developed two experimental tasks:
\begin{itemize}
	\item{Task 1:} subjects were presented with a visual representation of a spatial scene plus a linguistic description containing a CDSR and were tasked with drawing a polygon on the visual stimuli that defined the CDSR (or stated there was no such region).
	\item{Task 2:} subjects were presented with a visual representation of a spatial scene with a marked location and an accompanying spatial description and were asked to rate how well the location fitted with their understanding of the CDSR on a five point likert scale.
\end{itemize}

@@

%\subsection{Participants and Procedure}
%Using these stimuli pairs, we developed an online experiment with two different types of trials to explore our initial questions. 43 undergraduate students from two different third level institutes took part in the study. To control for sequence effects the presentation order of the trials were randomised for each participant as was the order of the stimuli presented within each trial.

\textbf{Participants and Procedure:} The experiment was delivered online. 43 undergraduate students from two third level institutes took part in the study. To control for sequence effects the order of the trials were randomised for each participant as was the order of the stimuli within each trial.
